Efficient pedigree recording for fast population genetics simulation

### 2017-12-30 forwards_paper.tex
Elaborate fig 5 caption

\include{macros}
\newcommand{\simupop}{\texttt{simuPOP}}
\newcommand{\fwdpp}{\texttt{fwdpp}}
\newcommand{\fwdpy}{\texttt{fwdpy11}}
\newcommand{\msprime}{\texttt{msprime}}
\newcommand{\ftprime}{\texttt{ftprime}}
\newcommand{\nodes}{\texttt{nodes}}
\newcommand{\edgesets}{\texttt{edgesets}}
\newcommand{\sites}{\texttt{sites}}
\newcommand{\mutations}{\texttt{mutations}}
\newcommand{\setdiff}{\smallsetminus}
\newcommand{\Nt}{\mathcal{N}}  % node table
\newcommand{\Et}{\mathcal{E}}  % edge table
\newcommand{\St}{\mathcal{S}}  % site table
\newcommand{\Mt}{\mathcal{M}}  % mutation table
\newcommand{\Al}{\mathcal{A}}  % list of ancestors
% mbox to avoid hyphenating
\newcommand{\taddnode}[1]{\mbox{\texttt{addnode}}(#1)}
\newcommand{\taddedge}[1]{\mbox{\texttt{addedge}}(#1)}
\newcommand{\tsimplify}[1]{\mbox{\texttt{simplify}}(#1)}
\DeclareMathOperator{\len}{length}
\DeclareMathOperator{\add}{add} % for adding to tables
\newcommand{\lleft}{\mathrm{left}}  % left label
\newcommand{\lright}{\mathrm{right}}
\newcommand{\lid}{\mathrm{id}}

@@

    \item
        In Python, using the \simupop{} library interfacing with Python code
	(via our package \ftprime{}),
        using a discrete but large number of sites.
        % $\mu$ and $r$ define per-base-pair mutation rate and we
        % defined the length of the simulated sequence, in base pairs, as $L = \tfrac{\rho}{4N \mu}$.
        % We varied $N \in (1000, 10000)$, $\rho \in (10^3, 10^4)$.

@@

\algstep{W1.}{Initialisation.}{
Set $\Nt \leftarrow \mbox{\texttt{NodeTable}}()$, $\mathcal{E}
\leftarrow \mbox{\texttt{EdgeTable}}()$, $t \leftarrow T$, and $j \leftarrow 0$.
 For $0 \leq k < N$, set $P_k \leftarrow \taddnode{\Nt, T}$.
}

@@

\subsection{Requirements for the \simupop{} implementation}

The simulations are implemented the Python package \ftprime{} 0.0.6rc0
which is available at \url{https://www.github.com/ashander/ftprime}.
Its requirements are encoded in an \texttt{environment.yml} file, compatible
with conda, but \msprime{} must be updated to the version listed below via pip
from GitHub \jda{TODO add command}.
In brief the requirements are:

\begin{enumerate}
    \item \msprime{} \jda{TODO add version from KRT's dev machine}
    \item \simupop{} 1.1.8.3
    \item python 3.5
\end{enumerate}

>>>>

\include{macros}
\newcommand{\simupop}{\texttt{simuPOP}}
\newcommand{\fwdpp}{\texttt{fwdpp}}
\newcommand{\fwdpy}{\texttt{fwdpy11}}
\newcommand{\msprime}{\texttt{msprime}}
\newcommand{\ftprime}{\texttt{ftprime}}
\newcommand{\nodes}{\texttt{nodes}}
\newcommand{\edgesets}{\texttt{edgesets}}
\newcommand{\sites}{\texttt{sites}}
\newcommand{\mutations}{\texttt{mutations}}
\newcommand{\setdiff}{\smallsetminus}
\newcommand{\Nt}{\mathcal{N}}  % node table
\newcommand{\Et}{\mathcal{E}}  % edge table
\newcommand{\St}{\mathcal{S}}  % site table
\newcommand{\Mt}{\mathcal{M}}  % mutation table
\newcommand{\Al}{\mathcal{A}}  % list of ancestors
\newcommand{\taddnode}[1]{\mbox{addnode}(#1)}
\newcommand{\taddedge}[1]{\mbox{addedge}(#1)}
\newcommand{\tsimplify}[1]{\mbox{simplify}(#1)}
\DeclareMathOperator{\len}{length}
\DeclareMathOperator{\add}{add} % for adding to tables
\newcommand{\lleft}{\mathrm{left}}  % left label
\newcommand{\lright}{\mathrm{right}}
\newcommand{\lid}{\mathrm{id}}

@@

    \item
        In Python, using the \simupop{} library interfacing with a custom Python library (\ftprime{}),
        using a discrete but large number of sites.
        % $\mu$ and $r$ define per-base-pair mutation rate and we
        % defined the length of the simulated sequence, in base pairs, as $L = \tfrac{\rho}{4N \mu}$.
        % We varied $N \in (1000, 10000)$, $\rho \in (10^3, 10^4)$.

@@

\algstep{W1.}{Initialisation.}{
Set $\Nt \leftarrow \mbox{NodeTable}()$, $\mathcal{E}
\leftarrow \mbox{EdgeTable}()$, $t \leftarrow T$, and $j \leftarrow 0$.
 For $0 \leq k < N$, set $P_k \leftarrow \taddnode{\Nt, T}$.
}

@@
